### 2015-09-15 vmcai-2016-tex/intro.tex
Fixed references in intro.tex

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
extend~\gsetxt{} principles to guarded value sets have failed to
produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

>>>>

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Other efforts to 
create heap inputs for guarded value set-based analysis 
techniques \cite{Dillig:2011,Xie:2005} have yet to
produce results provably equivalent to~\gsetxt{}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.
